What Happened to The Birth Rate?\thanks{Replication avaliable at \url{https://doi.org/10.48152/ssrp-mbxx-jm47}. Code and data avaliable at \url{https://github.com/cuilantao/Investigation-of-falling-US-Birth-Rates-since-the-great-recession}}

### 2022-02-28 outputs/paper/paper.Rmd
new change
Auto stash before merge of "main" and "origin/main"

Figure \@ref(fig:fig-LGBT-socioeconomic-indicators) shows some socioeconomic indicators classified by sexual orientation (LGBT or not), such as employment status, income level education level, and whether or not being insured and food insecure [@will_institute]. Darker color represents LGBT, lighter color represents non-LGBT.
From the plots, we can extract some socioeconomic indicators of LGBT. Comparing to non-LGBT population, LGBT are more likely to be unemployed, uninsured, being food insecure, having a low income (lower then $24k), and having a lower education level (percentage of LGBT population with Bachelor's or post-grad degree is slightly lower than that of the percentage of non-LGBT population).

@@

\newpage

# References

>>>>

Figure \@ref(fig:fig-LGBT-socioeconomic-indicators) shows some socioeconomic indicators classified by sexual orientation (LGBT or not), such as employment status, income level education level, and whether or not being insured and food insecure [@will_institute]. Darker color represents LGBT, lighter color represents non-LGBT.
From the plots, we can extract some socioeconomic indicators of LGBT. Comparing to non-LGBT population, LGBT population might be more likely to be unemployed, uninsured, being food insecure, having a low income (lower then $24k), and having a lower education level (percentage of LGBT population with Bachelor's or post-grad degree is slightly lower than that of the percentage of non-LGBT population). It's not rigorous to conclude that LGBT are more

@@

# Discussion

## Global Comparison

We do observe declination of world-wide birth rate despite of the impact level from recession. From the economic perspective, the countries who are least affected tend to have a stronger resistance to recession but not necessarily developed countries. While the most affected countries are mostly developing countries, they experienced a more significant plummet as percentage. It is also intriguing that the long-term births per 1000 people tend to converge to 10 for all countries mentioned above. However, the countries have higher resistance tend to delay the convergence which may derived from stronger economic status. Overall, the Great Recession was a turning point not only for the U.S. but also the whole world in the context of birth rate. The Great Recession may not be the direct cause of the world-wide declination in birth rates but it indeed provided an opportunity and provoked the desire for people to reconsider personal priorities with changed perspective of the society.

\newpage
# References

### 2022-02-28 outputs/paper/paper.tex
Auto stash before merge of "main" and "origin/main"

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\title{What Happened to The Birth Rate?\thanks{Replication avaliable at \url{https://doi.org/10.48152/ssrp-mbxx-jm47}. Code and data avaliable at \url{https://github.com/cuilantao/Investigation-of-falling-US-Birth-Rates-since-the-great-recession}}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{The Great Recession and the LGBT Movement}
\author{Lantao Cui \and Huakun Shen \and Sijian Wu}
\date{28 February 2022}

@@

Figure \ref{fig:fig-LGBT-socioeconomic-indicators} shows some socioeconomic indicators classified by sexual orientation (LGBT or not), such as employment status, income level education level, and whether or not being insured and food insecure (n.d.). Darker color represents LGBT, lighter color represents non-LGBT.
From the plots, we can extract some socioeconomic indicators of LGBT. Comparing to non-LGBT population, LGBT are more likely to be unemployed, uninsured, being food insecure, having a low income (lower then \$24k), and having a lower education level (percentage of LGBT population with Bachelor's or post-grad degree is slightly lower than that of the percentage of non-LGBT population).

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\title{What Happened to The Birth Rate?\thanks{Replication avaliable at \url{https://doi.org/10.48152/ssrp-mbxx-jm47}. Code and data avaliable at \url{https://github.com/cuilantao/Investigation-of-falling-US-Birth-Rates-since-the-great-recession}}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{The Great Recession and the LGBT Movement}
\author{Lantao Cui \and Huakun Shen \and Sijian Wu}
\date{27 February 2022}

@@

Figure \ref{fig:fig-LGBT-socioeconomic-indicators} shows some socioeconomic indicators classified by sexual orientation (LGBT or not), such as employment status, income level education level, and whether or not being insured and food insecure (n.d.). Darker color represents LGBT, lighter color represents non-LGBT.
From the plots, we can extract some socioeconomic indicators of LGBT. Comparing to non-LGBT population, LGBT population might be more likely to be unemployed, uninsured, being food insecure, having a low income (lower then \$24k), and having a lower education level (percentage of LGBT population with Bachelor's or post-grad degree is slightly lower than that of the percentage of non-LGBT population). It's not rigorous to conclude that LGBT are more
